---
title: "Scrapping Porsche Data from car-info"
author: "Xinqi Wang"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(rvest)
library(jsonlite)
library(xml2)
library(tidyverse)
library(ggplot2)
library(dplyr)
```
## Introduction:
In this exercise, I would like to scrape all the descriptions for the car brand "Porsche", including all its different models and trims form the website car-info. And import it as a data set, clean the data set, and finaly 
do some summary statistics on the data set.

## Writing out the functions
To do this, I first tried to scrape for one specific car:

```{r}
my_link <- 'https://www.car-info.com/en/model/porsche/918/918/spyder-4-6hyb-at-608-hp-4wd'
# Get all the specifications for one car
process_one_car <- function(my_link){
  t<- read_html(my_link)
  data_list<- list()
  data_list[['link']] <- my_link
  
  tkey <- t %>% html_nodes('.property') %>% html_text()
  tvalue <- t %>% html_nodes('.value') %>% html_text()
  
  if (length(tkey) == length(tvalue)){
    for (key_id in 1:length(tkey)){
      print(key_id)
      data_list[[  tkey[key_id]  ]] <- tvalue[key_id]
    }
  }
  return(data_list)
}
```

Next, I tried to create a function that gets all the links for the car brand:

```{r, message=FALSE, results=FALSE}
get_car_info <- function() {
  
  models_url <- "https://www.car-info.com/en/models/porsche"
  
  t2 <- read_html(models_url)
  
  type_urls <-unique( t2 %>% html_nodes(".col-md-4") %>% 
                        html_nodes('a') %>% 
                        html_attr('href'))
  type_urls <- paste0('https://www.car-info.com', type_urls)
  
  rel_link <- 'https://www.car-info.com/en/models/porsche/911'
  get_final_links <- function(rel_link) {
    t <- read_html(rel_link)
    to_full <- unique(paste0( "https://www.car-info.com", t %>% html_nodes(".background-white") %>% 
                                html_nodes("a") %>% html_attr("href")))
    my_full_urls <- NULL
    for (i in to_full) {
      # print(i)
      list_urls <- read_html(i)
      tep_full_link <- paste0( "https://www.car-info.com", list_urls %>% 
                                 html_nodes(".table-striped a" ) %>% html_attr("href"))
      my_full_urls <- c(my_full_urls, tep_full_link)
    }
    return(my_full_urls)
  }
  
  # full_911 <- get_final_links('https://www.car-info.com/en/models/porsche/911')
  
  all_urls <- lapply(type_urls, get_final_links)
  
  # print(all_urls)
  
  final_all_urls <- unlist(all_urls)
  
  res <- lapply(final_all_urls, process_one_car)
  res <- rbindlist(res, fill = T)
  return(res)
}
porsche <- get_car_info()

# save the raw data set 
# write.csv(porsche, file = '../Project 2/data/raw_data.csv')
```

## Data Cleaning
After getting the data set, I would also like to clean it. The data set has a lot of extra units after numerical variables and special characters in the NA variables.

``` {r,message=FALSE, warning=FALSE}
raw_df <- read.csv(file = '/Users/xinqi/Desktop/Coding2/Project 2/data/raw_data.csv')

raw_df <- separate(raw_df, Year, "-",
                  into = c("year"))


# Mutate all the numeric variables 
raw_df <- mutate(raw_df, 
                length = as.numeric(gsub("[^0-9\\.]", "", Length)),
                width = as.numeric(gsub("[^0-9\\.]", "", Width)),
                height = as.numeric(gsub("[^0-9\\.]", "", Height)),
                weight = as.numeric(gsub("[^0-9\\.]", "", Weight)),
                max_width = as.numeric(gsub("[^0-9\\.]", "", Max.width)),
                boot_capacity = as.numeric(gsub("[^0-9\\.]", "", Boot.capacity)),
                engine_kw = as.numeric(gsub("[^0-9\\.]", "", Engine.kw)),
                engine_hp = as.numeric(gsub("[^0-9\\.]", "", Engine.hp)),
                torque = as.numeric(gsub("[^0-9\\.]", "", Torque)),
                cylinders_diameter = as.numeric(gsub("[^0-9\\.]", "", Cylinders.diameter)),
                fuel_capacity = as.numeric(gsub("[^0-9\\.]", "", Fuel.capacity)),
                max_speed = as.numeric(gsub("[^0-9\\.]", "", Max.speed)),
                acceleration = as.numeric(gsub("[^0-9\\.]", "", Acceleration)),
                fuel_town = as.numeric(gsub("[^0-9\\.]", "", Fuel.town)),
                fuel_road = as.numeric(gsub("[^0-9\\.]", "", Fuel.road)),
                fuel_avg = as.numeric(gsub("[^0-9\\.]", "", Fuel.average)))

# Rename Variables:
raw_df <- rename(raw_df, 
                body_type = Body.type,
                fuel_supply = Fuel.supply,
                valves_in_cylinders = Valves.in.cylinders,
                eco_standart = Eco.standart,
                front_brakes = Front.brakes,
                rear_brakes = Rear.brakes)


# Replace all the '-' with NA
raw_df <- mutate(raw_df, doors = na_if(Doors, '-'),
                 seats = na_if(Seats, '-'),
                 fuel_supply = na_if(fuel_supply, '-'),
                 cylinders = na_if(Cylinders, '-'),
                 cylinders_diameter = na_if(cylinders_diameter, '-'),
                 valves_in_cylinders = na_if(valves_in_cylinders, '-'),
                 gears = na_if(Gears, '-'),
                 eco_standart = na_if(eco_standart, '-'),
                 ABS = na_if(ABS, '-'),
                 front_brakes = na_if(front_brakes, '-'),
                 rear_brakes = na_if(rear_brakes, '-'),
                 tires = na_if(Tires, '-'),
                 wheels = na_if(Wheels, '-'),
                 fuel_town = na_if(fuel_town, '-'))

# Clean up column tires and wheels
raw_df <- separate(raw_df, tires, " ",
                   into = c("tires"))

raw_df <- separate(raw_df, tires, ",",
                   into = c("tires"))

raw_df <- separate(raw_df, wheels, " ",
                   into = c("wheels"))

# Remove duplicate columns
raw_df <- select(raw_df, -c(X,Length,Width,Height,Weight,Max.width,Boot.capacity,Engine.kw,Engine.hp,Torque,Fuel.capacity,Max.speed,
                            Acceleration,Fuel.town,Fuel.road,Fuel.average,Tires,Wheels,Doors,Seats,Cylinders,Gears,Cylinders.diameter))

clean_df <- raw_df

# write.csv(clean_df, file = '../Project 2/data/clean_data.csv')

```
## EDA: Create some summary statistics plots of the data set.
There isn't too much data analysis we can do here with the data set as most of the information are on car specifications. However, I am interested to see some summary statistics of the variables in the data set.
First, I create a histogram shows the acceleration of different body types of Porsche. We can see that Porsche has 8 different body types in this data set, they are the Cabrio, Coupe, Fastback, Hatchback, Roadster, SUV, Targa, and Wagon. The average acceleration time for Porsche car is around 5.2 seconds, with the fastest body type are the  Cabrio, Coupe and Roadster.

``` {r, message=FALSE, echo=FALSE, warning=FALSE}
ggplot(data = clean_df, aes(x = acceleration, fill = body_type)) + 
  geom_histogram(aes(y = ..density..), alpha = 0.6) +
  labs(x = "Acceleration (in Seconds)", y = "Relative Frequency") +
  coord_cartesian(xlim = c(0, 13)) +
  geom_vline(data=clean_df, aes(xintercept=mean(clean_df$acceleration,na.rm=TRUE)),
             linetype="dashed")

```

Next, I am also curious to see what's the maximum speed of different body types of Porsche, so I did another histogram that shows the average maximum speed of all body types are around 270km/h, and the body type with highest maximum speed is Roadster.

``` {r, message=FALSE, echo=FALSE, warning=FALSE}
ggplot(data = clean_df, aes(x = max_speed, fill = body_type)) + 
  geom_histogram(aes(y = ..density..), alpha = 0.6) +
  labs(x = "Max Speed (km/h)", y = "Relative Frequency") +
  coord_cartesian(xlim = c(100, 380)) +
  geom_vline(data=clean_df, aes(xintercept=mean(clean_df$max_speed,na.rm=TRUE)),
             linetype="dashed")
```

Lastly, let's also take a look at the fuel capacity of each body type. The average fuel capacity of all types is around 76 liters, with the highest fuel capacity for Wagon and lowest fuel capacity for Hatchback. It's not too surprised to see that Wagons and SUVs have the highest fuel capacity, while the Cabrio and Coupe have the lowest.

``` {r, message=FALSE, echo=FALSE, warning=FALSE}
ggplot(data = clean_df, aes(x = fuel_capacity, fill = body_type)) + # here fill means filter
  geom_histogram(aes(y = ..density..), alpha = 0.6) +
  labs(x = "Fuel Capacity (in Liters)", y = "Relative Frequency") +
  coord_cartesian(xlim = c(40, 120)) +
  geom_vline(data=clean_df, aes(xintercept=mean(clean_df$fuel_capacity,na.rm=TRUE)),
             linetype="dashed")

```

## Conclusion
In this exercise, I created two functions that automatically scrape all the car specifications for all the models of Porsche, and then saved it as my raw data set. I later cleaned the data set with unwanted attributes of some variables like special characters in numerical values, and saved as my clean data set. In the end, I also did a few summery statistics graphs, which shows the average acceleration time for Porsche car is around 5.2 seconds, with the fastest body type are the Cabrio, Coupe and Roadster. In addition, the average maximum speed of all body types are around 270km/h, and the body type with highest maximum speed is Roadster. Finally, the average fuel capacity of all types is around 76 liters, with the highest fuel capacity for Wagon and lowest fuel capacity for Hatchback.

This is a very meaningful exercise because it enables the probablity of scrapping all the data from a website with writing a few lines of code in R. It would be also interesting to see other car-based market websites, and scrape the price information on different car models and types. This would be a great future exercise.